Results

### 2025-01-15 Analysis/04_Summarise_results.Rmd
added raw values

```{r}
# pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_2d.pdf", height = 11, width = 8.5)

# layout(matrix(1:(12*5), 12, 5))
# for(stressor in 1:5) {
#     ## For each stressor
#     plotting_data <- raw_results_2d[[stressor]]
#     ## Plot the metric
#     for(one_metric in 1:(ncol(plotting_data)/4)) {
#         ## Get the metric name
#         metric_name <- strsplit(colnames(selected_data), split = "_rm")[[1]][1]
#         ## Get the data
#         selected_data <- plotting_data[, 1:4]

#         ## Get the color TODO + add transparent
#         col <- rep("orange", 4)

#         ## Empty plot
#         plot(NULL, ylim = c(0, 5), xlim = quantile(c(selected_data), prob =  c(0.025, 0.975)), yaxt = "n", ylab = "", xlab = metric_name)

#         ## Add the lines
#         for(one_line in 1:4) {
#             ## Get the CIs and median
#             CIs <- quantile(selected_data[, one_line], prob = c(0.025, 0.25, 0.75, 0.975))
#             med <- median(selected_data[, one_line])
#             ## Plot the CIs
#             lines(y = rep(5-one_line, 2), x = CIs[c(1, 4)], lty = 3, col = col)
#             lines(y = rep(5-one_line, 2), x = CIs[c(2, 3)], lty = 1, col = col)
#             ## Plot the median
#             points(y =5-one_line, x = med, pch = 19, col = col)
#         }
#     }
# }

# fancy.plot(raw_results_2d, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = rep(19,5), xlab = "raw metric")
# dev.off()

# pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_4d.pdf", height = 11, width = 8.5)
# fancy.plot(raw_results_4d, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = rep(19,5), xlab = "raw metric")
# dev.off()

# pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_8d.pdf", height = 11, width = 8.5)
# fancy.plot(raw_results_8d, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = rep(19,5), xlab = "raw metric")
# dev.off()

# pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_emp.pdf", height = 11, width = 5.5)
# fancy.plot(raw_results_emp, col = col_vector, lm = NULL, null = NULL, metric.names = fancy_names, pch = c(19,15,17), xlab = "raw metric")
# dev.off()
```

>>>>

```{r}
plot.raw.data <- function(raw_data, names, levels = 4, col = c(rep("orange", 4), rep("darkgreen", 4), rep("blue", 4))) {

    n_stress <- length(raw_data)
    n_metric <- ncol(raw_data[[1]])/levels

    layout(matrix(0:((n_metric*n_stress)+n_stress+n_metric), n_metric+1, n_stress+1))

    ## Plot the rownames
    for(metric in 1:n_metric) {
        op <- par(mar = c(0,0,0,0), bty = "n")
        plot(NULL, xlim = c(0, 1), ylim = c(0,1), xaxt = "n", yaxt = "n", ylab = "", xlab = "")
        par(op)
        text(rev(names)[metric], x = 0.5, y = 0.5)  
    }

    for(stressor in 1:n_stress) {
        ## For each stressor
        plotting_data <- raw_data[[stressor]]

        ## Plot the stressor name
        op <- par(mar = c(0,0,0,0), bty = "n")
        plot(NULL, xlim = c(0, 1), ylim = c(0,1), xaxt = "n", yaxt = "n", ylab = "", xlab = "")
        par(op)
        text(names(raw_data)[stressor], x = 0.5, y = 0.5)

        ## Plot the metric
        for(one_metric in 1:n_metric) {
            ## Get the data
            selected_data <- plotting_data[, 1:levels]
            ## Remove the current data
            plotting_data <- plotting_data[, -c(1:levels)]

            ## Get the color TODO + add transparent
            col_selected <- col[one_metric]
            colours <- rev(sapply(seq(from = 0.2, to = 1, length.out = levels), function(x, col) adjustcolor(col_selected, alpha.f = x), col = col_selected))

            ## Empty plot
            op <- par(mar = c(2,2,2,2), bty = "n")
            plot(NULL, ylim = c(0, 5), xlim = quantile(c(selected_data), prob =  c(0.025, 0.975)), yaxt = "n", ylab = "", xlab = "")

            ## Add the lines
            for(one_line in 1:levels) {
                ## Get the CIs and median
                CIs <- quantile(selected_data[, one_line], prob = c(0.025, 0.25, 0.75, 0.975))
                med <- median(selected_data[, one_line])
                ## Plot the CIs
                lines(y = rep(5-one_line, 2), x = CIs[c(1, 4)], lty = 3, col = colours[one_line])
                lines(y = rep(5-one_line, 2), x = CIs[c(2, 3)], lty = 1, col = colours[one_line])
                ## Plot the median
                points(y =5-one_line, x = med, pch = 19, col = colours[one_line])
            }
            par(op)
        }
    }
}

pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_2d.pdf", height = 22.6661, width = 17)
plot.raw.data(raw_results_2d, names = fancy_names, levels = 4, col = c(rep("orange", 4), rep("darkgreen", 4), rep("blue", 4)))
dev.off()

pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_4d.pdf", height = 22.6661, width = 17)
plot.raw.data(raw_results_4d, names = fancy_names, levels = 4, col = c(rep("orange", 4), rep("darkgreen", 4), rep("blue", 4)))
dev.off()

pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_8d.pdf", height = 22.6661, width = 17)
plot.raw.data(raw_results_8d, names = fancy_names, levels = 4, col = c(rep("orange", 4), rep("darkgreen", 4), rep("blue", 4)))
dev.off()

pdf(file = "../Manuscript/Figures/raw_results_per_metric_per_stressor_emp.pdf", height = 22.6661, width = 10.2)
plot.raw.data(raw_results_emp, names = fancy_names, levels = 2, col = c(rep("orange", 4), rep("darkgreen", 4), rep("blue", 4)))
dev.off()
